---
title: "Coding workshop: Week 10"
author: "Veronique Letourneau"
format:
  html:
    toc: true
    toc-location: left
    code-fold: true
execute:
  message: false
  warning: false
---

```{r set-up}
# model packages
library(MASS) # have to read this in before tidyverse 
library(lme4)
library(glmmTMB) # ok if you don't have this - just comment it out

# diagnostics and model info
library(DHARMa)
library(MuMIn)
library(ggeffects)
library(lmtest)
library(broom)

# general usage
library(tidyverse)
library(here)
library(naniar)
library(skimr)
library(GGally)
library(flextable)

salamanders <- read_csv(here("data", "Salamanders.csv"))
```

# Data info from `glmmTMB`:

`site`: name of a location where repeated samples were taken  
`mined`: factor indicating whether the site was affected by mountain top removal coal mining  
`cover`: amount of cover objects in the stream (scaled)  
`sample`: repeated sample  
`DOP`: Days since precipitation (scaled)  
`Wtemp`: water temperature (scaled)  
`DOY`: day of year (scaled)  
`spp`: abbreviated species name, possibly also life stage  
`count`: number of salamanders observed  

scaled variables: helpful for very different numbers, like temperature and days 
of the year (mean of continuous ans shifting variables on to the center *of the mean*)

# Explore the data set:

## histogram of counts:

```{r histogram}
ggplot(data = salamanders, aes(x = count)) +
  geom_histogram(bins = 17)
```

## Missingness:

```{r missingness}
gg_miss_var(salamanders)
```

## Skim: 

```{r skim-dataset}
skim(salamanders)
```

## Pairs plot:  

```{r pairs-plot}
#| fig.width: 12
#| fig.height: 12
#| out.width: 90%
#| fig.align: center

salamanders %>% 
  # taking out the site column
  select(!site) %>% 
  ggpairs
```

# Question: How does salamander count vary with mined status, species, and stream cover?

## Build models

```{r models}
# linear model, we know this is wrong (count as response not good for linear) 
salmod1 <- lm(count ~ cover + mined + spp, data = salamanders)

# generalized linear model with Poisson distribution *mean and variance are the same*
salmod2 <- glm(count ~ cover + mined + spp, data = salamanders, family = "poisson")

# generalized linear model with negative binomial distribution (no family, glm.nb = negative binomial). *good for over-dispersion*
salmod3 <- glm.nb(count ~ cover + mined + spp, data = salamanders)

# generalized linear model with Poisson distribution and random effect of site


# generalized linear model with negative binomial distribution and random effect of site

```

## Look at residuals

```{r model-residuals}
#| fig.height: 6
#| fig.width: 8
#| fig.align: center

# check diagnostics
simulateResiduals(salmod1, plot = TRUE)
simulateResiduals(salmod2, plot = TRUE)
simulateResiduals(salmod3, plot = TRUE)
```

## Which distribution to use?
Model 3 (generalized linear model with negative binomial distribution), but we can still use model selection to double check (2 ways to choose which distribution to use: looking at diagnostics and model selection)

```{r choosing-model}
model.sel(salmod1, salmod2, salmod3)
```

## Model summary

```{r summaries}
# model object
salmod3

# summary 
summary(salmod3)
# shows that cover is not a significant predictor, count is lower on mined and higher in unmined)
# confidence intervals
confint(salmod3)

# adjusted R2 (only look at delta R2m) *low because we're only looking at 3 predictors*
r.squaredGLMM(salmod3)
```

```{r}
# model object in table
salmod3 %>% 
  as_flextable()
```

```{r}
# another one
tidy(salmod3) %>% 
  flextable()
```

## Visualizing:

```{r visualization}
#| fig.width: 12
#| fig.height: 10
#| out.width: 90%
#| fig.align: center
plot(ggpredict(salmod3, terms = c("cover", "mined")), add.data = TRUE)
# shows that cover has no significant effect

plot(ggpredict(salmod3, terms = c("cover", "mined", "spp")), add.data = TRUE)
# shows that species has a significant effect on the number of salamanders, but mined ans unmined still remains the main significance
```

