---
title: "Coding workshop: Week 10"
author: "your name here"
format:
  html:
    toc: true
    toc-location: left
    code-fold: true
execute:
  message: false
  warning: false
---

```{r set-up}
# model packages
library(MASS) # have to read this in before tidyverse 
library(lme4)
library(glmmTMB) # ok if you don't have this - just comment it out

# diagnostics and model info
library(DHARMa)
library(MuMIn)
library(ggeffects)
library(lmtest)
library(broom)

# general usage
library(tidyverse)
library(here)
library(naniar)
library(skimr)
library(GGally)
library(flextable)

salamanders <- read_csv(here("data", "salamanders.csv"))
```

# Data info from `glmmTMB`:

`site`: name of a location where repeated samples were taken  
`mined`: factor indicating whether the site was affected by mountain top removal coal mining  
`cover`: amount of cover objects in the stream (scaled)  
`sample`: repeated sample  
`DOP`: Days since precipitation (scaled)  
`Wtemp`: water temperature (scaled)  
`DOY`: day of year (scaled)  
`spp`: abbreviated species name, possibly also life stage  
`count`: number of salamanders observed  

# Explore the data set:

## histogram of counts:

```{r histogram}

```

## Missingness:

```{r missingness}

```

## Skim: 

```{r skim-dataset}

```

## Pairs plot:  

```{r pairs-plot}
#| fig.width: 12
#| fig.height: 12
#| out.width: 90%
#| fig.align: center


```

# Question: How does salamander count vary with mined status, species, and stream cover?

## Build models

```{r models}
# linear model, we know this is wrong


# generalized linear model with Poisson distribution


# generalized linear model with negative binomial distribution


# generalized linear model with Poisson distribution and random effect of site


# generalized linear model with negative binomial distribution and random effect of site

```

## Look at residuals

```{r model-residuals}
#| fig.height: 6
#| fig.width: 8
#| fig.align: center

# check diagnostics

```

## Which distribution to use?

```{r choosing-model}

```

## Model summary

```{r summaries}
# model object


# summary 


# confidence intervals


# adjusted R2

```

```{r}
# model object in table

```


## Visualizing:

```{r visualization}
#| fig.width: 12
#| fig.height: 10
#| out.width: 90%
#| fig.align: center


```

